---
title: "data import and cleaning for epic app"
author: "John Chapman"
date: "July 10, 2019"
output: html_document
---

load packages
```{r}
library(RSQLite)
library(dplyr)
library(readr)

```


## Import Data

location of "epicdb.sqlite" file on GoldenParish:
"~/OneDrive - Southern Virginia University/R-Studio/EPIC/data/epicdb.sqlite"
```{r}
sqlitePath <- "~/OneDrive - Southern Virginia University/R-Studio/EPIC/data/epicdb.sqlite"
table <- "master1"
```

## loadData and saveData functions
```{r}
saveData <- function(data) {
  # Connect to the database
  db <- dbConnect(SQLite(), sqlitePath)
  # Construct the update query by looping over the data fields
  query <- sprintf(
    "INSERT INTO %s (%s) VALUES ('%s')",
    table, 
    paste(names(data), collapse = ", "),
    paste(data, collapse = "', '")
  )
  # Submit the update query and disconnect
  dbGetQuery(db, query)
  dbDisconnect(db)
}

loadData <- function(table) {
  # Connect to the database
  db <- dbConnect(SQLite(), sqlitePath)
  # Construct the fetching query
  query <- sprintf("SELECT * FROM %s", table)
  # Submit the fetch query and disconnect
  data <- dbGetQuery(db, query)
  dbDisconnect(db)
  data
}

```

Call the loadData Function:
```{r}
system.time(master1 <- loadData(table)) # 22.987 seconds

```

Create a vector of occupation categories
```{r}

```


create a vector of degree categories
```{r}

```


Is it true that a high amount of employees in a given occupation (with a specific degree) is also an indication that there is an institution granting those degrees near by? (this is probably not necessarily an indicator of rank--in the degree--but it could be useful for internship or changing companies)

What is the value of identifying these occupation-degree clusters by geography/area?
Is there a difference in salary or opportunities or job security for pursuing an occupation in an occupation-degree cluster rather than an occupation/degree combination outside of a geographic cluster area?
Do these occupation-degree clusters even exist?
Do they change over time?  Do they migrate/move?


What data do I need?
Occupation data by MSA 
CIP degrees (by number granted?) by MSA (?)



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
